Modeling choices

### 2021-11-19 analysis/03_laws-repression.Rmd
Remove all civlib and clphy models

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(broom.mixed)
library(tidybayes)
library(glue)
library(brms)
library(scales)
library(kableExtra)
library(modelsummary)
library(lubridate)
library(here)

@@

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new,
             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding))

  # Load regression tables
  tar_load(c(models_tbl_e1a_re, models_tbl_e1b_re, 
             models_tbl_e1c_re, models_tbl_e1d_re))

@@

```{r tbl-e1a-re}
# Build nicer column names
models_for_table_e1a_re <- models %>% 
  filter(outcome_var == "Political terror") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

# Make a named vector of original model names and nice names
models_names_table_e1a_re <- models_for_table_e1a_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1a_re$model)

# Rename the columns
names(models_tbl_e1a_re) <- recode(names(models_tbl_e1a_re), 
                                   !!!models_names_table_e1a_re)

modelsummary(models_tbl_e1a_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

@@

# E~1b~: NGO laws and physical violence

@@

```{r tbl-e1b-re}
models_for_table_e1b_re <- models %>% 
  filter(outcome_var == "Physical violence") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

model_names_tbl_e1b_re <- models_for_table_e1b_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1b_re$model)

names(models_tbl_e1b_re) <- recode(names(models_tbl_e1b_re), 
                                   !!!model_names_tbl_e1b_re)

modelsummary(models_tbl_e1b_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

@@

```{r plot-coefs-e1b}
coef_plots <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

```{r plot-mfx-e1b}
plot_clphy_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clphy_total", "barriers_total", "Total legal barriers",
  "m_clphy_total_new", "barriers_total_new", "New legal barriers",
  "m_clphy_advocacy", "advocacy", "Advocacy",
  "m_clphy_entry", "entry", "Entry",
  "m_clphy_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

mfx <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "new|baseline")) %>% 
  left_join(plot_clphy_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted physical violence index\n(higher values = less violence)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

# E~1c~: NGO laws and civil liberties

```{r tbl-e1c-re}
models_for_table_e1c_re <- models %>% 
  filter(outcome_var == "Private civil liberties") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

model_names_tbl_e1c_re <- models_for_table_e1c_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1c_re$model)

names(models_tbl_e1c_re) <- recode(names(models_tbl_e1c_re), 
                                   !!!model_names_tbl_e1c_re)

modelsummary(models_tbl_e1c_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

```{r plot-coefs-e1c}
coef_plots <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

```{r plot-mfx-e1c}
plot_clpriv_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clpriv_total", "barriers_total", "Total legal barriers",
  "m_clpriv_total_new", "barriers_total_new", "New legal barriers",
  "m_clpriv_advocacy", "advocacy", "Advocacy",
  "m_clpriv_entry", "entry", "Entry",
  "m_clpriv_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

mfx <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "new|baseline")) %>% 
  left_join(plot_clpriv_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted civil liberties index\n(higher values = better protection)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

# E~1d~: NGO laws and latent physical integrity rights

```{r tbl-e1d-re}
models_for_table_e1d_re <- models %>% 
  filter(outcome_var == "Latent human rights") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

model_names_tbl_e1d_re <- models_for_table_e1d_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1d_re$model)

names(models_tbl_e1d_re) <- recode(names(models_tbl_e1d_re), 
                                   !!!model_names_tbl_e1d_re)

modelsummary(models_tbl_e1d_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

```{r plot-coefs-e1d}
coef_plots <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

```{r plot-mfx-e1d}
plot_lhr_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_lhr_total", "barriers_total", "Total legal barriers",
  "m_lhr_total_new", "barriers_total_new", "New legal barriers",
  "m_lhr_advocacy", "advocacy", "Advocacy",
  "m_lhr_entry", "entry", "Entry",
  "m_lhr_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted latent human rights value\n(higher values = better human rights)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

>>>>

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(glue)
library(brms)
library(scales)
library(kableExtra)
library(modelsummary)
library(here)

@@

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding,
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding))

  # Load regression tables
  tar_load(c(models_tbl_e1a, models_tbl_e1b))

@@

```{r tbl-e1a-re}
# Build nicer column names
models_for_table_e1a <- models %>% 
  filter(outcome_var == "Political terror") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

# Make a named vector of original model names and nice names
models_names_table_e1a <- models_for_table_e1a %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1a$model)

# Rename the columns
names(models_tbl_e1a) <- recode(names(models_tbl_e1a), 
                                !!!models_names_table_e1a)

modelsummary(models_tbl_e1a,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

@@

# E~1b~: NGO laws and latent human rights

@@

```{r tbl-e1b}
models_for_table_e1b <- models %>% 
  filter(outcome_var == "Latent human rights") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))

model_names_tbl_e1b <- models_for_table_e1b %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1b$model)

names(models_tbl_e1b) <- recode(names(models_tbl_e1b), 
                                !!!model_names_tbl_e1b)

modelsummary(models_tbl_e1b,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

@@

```{r plot-coefs-e1b}
coef_plots <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "baseline")) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = "none", alpha = "none") +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  theme_ngo()
```

@@

```{r plot-mfx-e1b}
plot_lhr_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_lhr_total", "barriers_total", "Total legal barriers",
  "m_lhr_total_new", "barriers_total_new", "New legal barriers",
  "m_lhr_advocacy", "advocacy", "Advocacy",
  "m_lhr_entry", "entry", "Entry",
  "m_lhr_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = "none") +
  labs(x = "Count of legal barriers",
       y = "Predicted latent human rights value\n(higher values = better human rights)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

### 2021-11-19 analysis/03_model-details.Rmd
Remove all civlib and clphy models

  # This also works but again doesn't register correctly as dependencies
  # tar_load(starts_with("m_clpriv"))

  # So we do it this manual way
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_v2csreprss, 
             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clphy_v2csreprss, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new, 
             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_clpriv_v2csreprss, 
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding, 
             m_lhr_v2csreprss, 
             m_pts_baseline_train, m_pts_total_train, 
             m_pts_advocacy_train, m_pts_entry_train, m_pts_funding_train, 
             m_pts_v2csreprss_train, 
             m_clphy_baseline_train, m_clphy_total_train, 
             m_clphy_advocacy_train, m_clphy_entry_train, m_clphy_funding_train, 
             m_clphy_v2csreprss_train, 
             m_clpriv_baseline_train, m_clpriv_total_train, 
             m_clpriv_advocacy_train, m_clpriv_entry_train, m_clpriv_funding_train, 
             m_clpriv_v2csreprss_train))
})
```

```{r set-computer-details}
computer <- "Work"

if (computer == "Work") {
  computer_details <- "2019 MacBook Pro with 16 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
} else {
  computer_details <- "2016 MacBook Pro with 4 cores and 16 GB of RAM, using Stan through brms through cmdstanr"
}
```

@@

## Models for E~1~ (civil society laws)

@@

## Models for E~2~ (civil society environment)

@@

- `R/models_pts.R` (for PTS-based models)
- `R/models_clphy.R` (for V-Dem physical violence-based models)
- `R/models_clpriv.R` (for V-Dem private civil liberties-based models)
- `R/models_lhr.R` (for latent human rights-based models)

@@

#### `R/models_clphy.R`

```{r, code=xfun::read_utf8(here::here("R", "models_clphy.R")), eval=FALSE, class.source="fold-hide"}
```

#### `R/models_clpriv.R`

```{r, code=xfun::read_utf8(here::here("R", "models_clpriv.R")), eval=FALSE, class.source="fold-hide"}
```

>>>>

  # This also works but again doesn't register correctly as dependencies
  # tar_load(starts_with("m_pts"))

  # So we do it this manual way
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_v2csreprss, 
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding, 
             m_lhr_v2csreprss, 
             m_pts_baseline_train, m_pts_total_train, 
             m_pts_advocacy_train, m_pts_entry_train, m_pts_funding_train, 
             m_pts_v2csreprss_train,
             m_lhr_baseline_train, m_lhr_total_train, m_lhr_total_new_train, 
             m_lhr_advocacy_train, m_lhr_entry_train, m_lhr_funding_train, 
             m_lhr_v2csreprss_train))
})
```

```{r set-computer-details}
computer <- "Personal"

if (computer == "Work") {
  computer_details <- "2019 MacBook Pro with 16 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
} else {
  computer_details <- "2021 MacBook Pro M1 Max with 10 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
}
```

@@

## Models for E~1~ (de jure civil society laws)

@@

## Models for E~2~ (de facto civil society environment)

@@

- `R/models_pts.R` (for PTS-based models)
- `R/models_lhr.R` (for latent human rights-based models)

@@

### 2021-11-19 analysis/03_modeling-choices.Rmd
Remove all civlib and clphy models

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(janitor)
library(brms)
library(lme4)
library(lmtest)  # For log ratio tests
library(performance)  # For ICCs
library(scales)
library(modelsummary)
library(here)

CHAINS <- 4
ITER <- 2000
WARMUP <- 1000
BAYES_SEED <- 1234

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr")

@@

  canary <- tar_read(panel_lagged)
})
```

# Interpretation reminders

@@

```{r null-models}
m0_pts <- lmer(PTS_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
m0_clphy <- lmer(v2x_clphy_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
m0_clpriv <- lmer(v2x_clpriv_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
```

@@

```{r icc-models}
# This shows just the ICC. modelsummary() helpfully includes it.
# icc(m0_pts)

modelsummary(list(m0_pts, m0_clphy, m0_clpriv),
             estimate = "{estimate}", statistic = NULL,
             gof_map = list(list("raw" = "icc", "clean" = "ICC", "fmt" = 4)))
```

These values represent the variation in the outcome variable that can be explained by the country/year structure, which is a *ton*! For the PTS model, for instance, the ICC is `r round(icc(m0_pts)$ICC_adjusted, 4)`, meaning that the random effects structure explains `r percent(icc(m0_pts)$ICC_adjusted)` of the variation in PTS.

@@

```{r icc-models-by-group}
icc(m0_pts, by_group = TRUE)
icc(m0_clphy, by_group = TRUE)
icc(m0_clpriv, by_group = TRUE)
```

@@

```{r basic-model}
# First we add the main variable of interest (civil society repression here)
m1 <- lmer(PTS_lead1 ~ v2csreprss + (1 | year) + (1 | gwcode),
           REML = FALSE, data = canary)
modelsummary(list("Null model" = m1),
             coef_omit = "sd__")
```

@@

modelsummary(list("Null model" = m1, "Within/between model" = m2),
             coef_omit = "sd__")
```

@@

>>>>

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(lme4)
library(lmtest)  # For log ratio tests
library(performance)
library(modelsummary)
library(scales)
library(janitor)
library(here)

@@

  canary <- tar_read(panel_lagged)
})

# Goodness-of-fit measures to include
gm <- tribble(
  ~raw, ~clean, ~fmt,
  "nobs", "Num.Obs.", 3,
  "icc", "ICC", 3
)
```

@@

```{r null-models}
m0_pts <- lmer(PTS_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
m0_lhr <- lmer(latent_hr_mean_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
```

@@

```{r icc-models}
modelsummary(list(m0_pts, m0_lhr),
             estimate = "{estimate}", statistic = NULL,
             group = group + term ~ model,
             gof_map = gm)
```

These values represent the variation in the outcome variable that can be explained by the country/year structure, which is a *ton*! For the PTS model, for instance, the ICC is `r round(performance::icc(m0_pts)$ICC_adjusted, 4)`, meaning that the random effects structure explains `r percent(performance::icc(m0_pts)$ICC_adjusted)` of the variation in PTS.

@@

```{r icc-models-by-group}
performance::icc(m0_pts, by_group = TRUE)
performance::icc(m0_lhr, by_group = TRUE)
```

@@

```{r basic-model}
# First we add the main variable of interest (civil society repression here)
m1 <- lmer(PTS_lead1 ~ v2csreprss + (1 | year) + (1 | gwcode),
           REML = FALSE, data = canary)
modelsummary(list("Null model" = m1),
             group = group + term ~ model,
             coef_omit = "sd__", gof_map = gm)
```

@@

modelsummary(list("Null model" = m1, "Within/between model" = m2),
             group = group + term ~ model,
             coef_omit = "sd__", gof_map = gm)
```

@@

## Interpretation reminders

NB: We ultimately don't use this within/between difference since the random effects within/between models take forever to run and provide no improvement over the more basic models, but I'll keep this here as a reminder to future me in future projects:
